\documentclass[margin,line,11pt]{resume}
 
\usepackage[latin1]{inputenc}
\usepackage[english,french]{babel}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}
\usepackage{graphicx,wrapfig}
\usepackage{url}
\usepackage[colorlinks=true, pdfstartview=FitV, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
\pdfcompresslevel=9

\edef\hc{\string:} % \hc prints a normal colon
\edef\hs{\string;} % \hs prints a normal semicolon

\begin{document}{\Huge \textbf{Alex Pandya}}
\begin{resume}

%============ Contact info ==========================%

\section{\mysidestyle Contact\\Information}

\faHome \space Cornell Center for Astrophysics and Planetary Science \hfill \faEnvelope\hspace{0.7mm} \href{mailto:alex.pandya@cornell.edu}{alex.pandya@cornell.edu} \hspace{3.8mm} \hphantom{.}\\
\hphantom{.}\hspace{3.5mm} Space Sciences Building \hfill \faGithub \hspace{1.2mm} \href{https://github.com/aapandy2}{github.com/aapandy2} \hspace{9mm}\hphantom{.}\\
\hphantom{.}\hspace{3.5mm} 122 Sciences Dr. \hfill \faTv \hspace{0.5mm} \href{https://aapandy2.github.io/}{aapandy2.github.io}\hspace{15mm}\hphantom{.}\\
\hphantom{.}\hspace{3.7mm} Ithaca, NY 14850 \hfill \faLinkedin \hspace{1mm} \href{https://linkedin.com/in/alexpandya}{linkedin.com/in/alexpandya}\hspace{0mm}\hphantom{.} \\ 

%============ Research interests =================%

\section{\mysidestyle Research Interests}

I am broadly interested in \textbf{high-energy astrophysical systems}, \textbf{strong-field gravity}, and \textbf{computational physics}.  

Specific topics of interest include \textit{relativistic viscous fluids}, \textit{black holes}, \textit{neutron stars}, \\
\textit{numerical PDE}, and \textit{high-performance computing}, to name a few.
\vspace{5mm}

%============= Employment ===========================%

\section{\mysidestyle Professional Experience}

\textbf{Cornell University}\hfill 2023--Present\\
\textit{Postdoctoral Associate}, Center for Astrophysics and Planetary Science \vspace{2mm}\\
\textbf{Princeton University}\hfill 2019--2023\\
\textit{NSF Graduate Research Fellow} \vspace{2mm} \\
\textbf{University of Illinois at Urbana-Champaign (UIUC)}\hfill 2014--2017\\
\textit{Undergraduate Researcher}\\
\vspace{2mm}

%============= Education ===========================%

\section{\mysidestyle Education}

\textbf{Princeton University}\hfill 2019--2023\\
\textit{Ph.D. in Physics}\\
Dissertation\hc \, ``Toward astrophysics applications of causal, stable \\ 
\hphantom{.}\hspace{24mm}relativistic dissipative hydrodynamics''\\
Advisor\hc ~Prof. Frans Pretorius \vspace{2mm}\\ 
\textbf{Princeton University}\hfill 2017--2019\\
\textit{M.A. in Physics}\vspace{2mm} \\ 
\textbf{University of Illinois at Urbana-Champaign (UIUC)}\hfill 2013--2016\\
\textit{B.S. in Physics}\\
Minor\hc ~\textit{Mathematics}
\vspace{2mm}
 
%================== Honors and awards ==================%

\section{\mysidestyle Grants, awards, \& scholarships}

\textbf{Kusaka Memorial Prize in Physics} \hfill 2022 \\
\textit{Award for ``outstanding performance in research and professional promise''\hs\, \$3,000.} \\
Department of Physics, Princeton University\vspace{2mm} \\
\textbf{NSF Graduate Research Fellowship} \hfill 2019--2022 \\
\textit{Competitive national fellowship grant totaling \$138,000.}\\
US National Science Foundation\vspace{2mm} \\
\textbf{Honorable Mention, Computational Science Graduate Fellowship} \hfill 2017 \\
\textit{Competitive national fellowship waitlist/honorable mention.} \\
US Department of Energy\vspace{2mm} \\
\textbf{Robert E. Hetrick Outstanding Senior Thesis Award} \hfill 2017 \\
\textit{Award recognizing ``outstanding independent research by an undergraduate''\hs\, \$250.} \\
Department of Physics, UIUC\vspace{2mm} \\
\clearpage
\textbf{Member, Phi Beta Kappa Honor Society} \hfill 2016 \\
UIUC\vspace{2mm} \\
\textbf{National STEM Scholarship} \hfill 2016 \\
\textit{Winner of a national scholarship competition for STEM undergrads\hs\, \$5,000.} \\
LGS Innovations LLC\vspace{2mm} \\
\textbf{Dean's List} \hfill 2013--2016 \\
UIUC\vspace{2mm} \\
\textbf{Lorella M. Jones Summer Research Fellowship} \hfill 2015 \\
\textit{Fellowship supporting summer research ``for outstanding undergraduates''\hs\, \$2,500.}\\
Department of Physics, UIUC\vspace{2mm}\\
\textbf{Chancellor's Scholarship} \hfill 2013--2014 \\
\textit{Merit scholarship for incoming freshmen\hs\, \$1,000.} \\
UIUC\vspace{2mm} \\
\textbf{N. \& D. Waffle Scholarship} \hfill 2013 \\
\textit{Merit scholarship for incoming freshman in the College of Agriculture\hs\, \$2,000.} \\
Department of Crop Sciences, UIUC

%\clearpage

%================ Publications =====================%
\section{\mysidestyle Publications}
\begin{enumerate}
\item \textbf{Alex Pandya}, Elias R. Most, Frans Pretorius, ``Causal, stable first-order viscous relativistic hydrodynamics with ideal gas microphysics'' \textit{Phys. Rev. D} \textbf{106} 123036 \href{https://arxiv.org/abs/2209.09265}{arXiv\hc2209.09265} (2022).
	
\item \textbf{Alex Pandya}, Justin L. Ripley, ``Dynamics of a nonminimally coupled scalar field in asymptotically $\textnormal{AdS}_{4}$ spacetime'' \textit{Class. Quantum Grav.} \href{https://arxiv.org/abs/2206.08854}{arXiv\hc2206.08854} (2022).
\vspace{1mm}

\item \textbf{Alex Pandya}, Elias R. Most, Frans Pretorius, ``Conservative finite volume scheme for first-order viscous relativistic hydrodynamics'' \textit{Phys. Rev. D} \textbf{105} 123001 \href{https://arxiv.org/abs/2201.12317}{arXiv\hc2201.12317} (2022).
\vspace{1mm}

\item Andrew Marszewski, Ben S. Prather, Abhishek V. Joshi, \textbf{Alex Pandya}, Charles F. Gammie, ``Updated Transfer Coefficients for Magnetized Plasmas'' \textit{ApJ}, 921\hc17 \href{https://arxiv.org/abs/2108.10359}{arXiv\hc2108.10359} (2021). \vspace{1mm}

\item \textbf{Alex Pandya}, Frans Pretorius, ``Numerical exploration of first-order relativistic hydrodynamics'' \textit{Phys. Rev. D} \textbf{104} 023015 \href{https://arxiv.org/abs/2104.00804}{arXiv\hc2104.00804} (2021).
\vspace{1mm}

\item \textbf{Alex Pandya}, Frans Pretorius, ``The Rotating Black Hole Interior\hc\, Insights from Gravitational Collapse in $AdS_3$'' \textit{Phys. Rev. D} \textbf{101} 104026, \href{https://arxiv.org/abs/2002.07130}{arXiv\hc2002.07130} (2020).
\vspace{1mm}

\item \textbf{Alex Pandya}, Mani Chandra, Abhishek Joshi, Charles F. Gammie, ``Numerical Evaluation of the Relativistic Magnetized Plasma Susceptibility Tensor and Faraday Rotation Coefficients" \textit{ApJ}, 868\hc13 \href{https://arxiv.org/abs/1810.05530}{arXiv\hc1810.05530} (2018).
\vspace{1mm}

\item \textbf{Alex Pandya}, Zhaowei Zhang, Mani Chandra, Charles F. Gammie, ``Polarized Synchrotron Emissivities and Absorptivities for Relativistic Thermal, Power-Law, and Kappa Distribution Functions" \textit{ApJ}, 822\hc34 \href{https://arxiv.org/abs/1602.08749}{arXiv\hc1602.08749} (2016).
\end{enumerate}

%============= Invited talks =================%
\vspace{2mm}
\section{\mysidestyle Invited talks}

\textbf{Nuclear Theory Group Seminar}, \textit{Bielefeld University} (virtual) \hfill February 2023 \\
``Finite volume methods for relativistic dissipative hydrodynamics'' \vspace{2mm} \\
\textbf{Strong Gravity Seminar}, \textit{Perimeter Institute for Theoretical Physics} \hfill January 2023 \\
``On dissipation in relativistic fluid theories'' \vspace{2mm} \\
\textbf{Numerical Relativity Community Call}, \textit{SXS Collaboration} (virtual) \hfill December 2022 \\
``Numerical methods for first-order viscous relativistic hydrodynamics'' \vspace{2mm} \\
\clearpage
\textbf{PDE Seminar}, \textit{Vanderbilt University Dept. of Mathematics} \hfill April 2022 \\
``Initial investigations of causal, stable first-order relativistic hydrodynamics'' \vspace{2mm} \\
\textbf{Medium \& High Energy Physics Seminar}, \textit{UIUC Dept. of Physics} \hfill January 2022 \\
``Initial investigations of causal, stable first-order relativistic hydrodynamics'' \\

%============= Conferences and Workshops =================%
\vspace{2mm}
\section{\mysidestyle Conferences \\ \& Workshops}

\textbf{APS April Meeting}, \textit{Minneapolis, MN} \hfill April 2023\\
\textit{Contributed talk}, ``Modeling neutron stars using first-order \\
\hphantom{.}\hspace{30mm}viscous relativistic hydrodynamics'' \vspace{2mm} \\
\textbf{Numerical Relativity Community Summer School}, \textit{Providence, RI} \hfill August 2022\vspace{2mm}\\
\textbf{APS April Meeting}, \textit{New York, NY} \hfill April 2022\\
\textit{Contributed talk}, ``Conservative finite volume scheme for BDNK \\
\hphantom{.}\hspace{30mm}relativistic dissipative hydrodynamics'' \vspace{2mm} \\
\textbf{APS April Meeting}, \textit{Online} \hfill April 2021\\
\textit{Contributed talk}, ``Numerical methods for relativistic dissipative fluids'' \vspace{2mm} \\
\textbf{APS April Meeting}, \textit{Online} \hfill April 2020\\
\textit{Contributed talk}, ``The Rotating Black Hole Interior\hc\, Insights from \\
\hphantom{.}\hspace{28mm} Gravitational Collapse in (2+1)D'' \vspace{2mm} \\
\textbf{UIUC Undergraduate Research Symposium}, \textit{Champaign, IL} \hfill April 2016\\
\textit{Poster presentation}, ``Polarized Synchrotron Emissivities and \\
\hphantom{.}\hspace{34mm} Absorptivities for Relativistic Thermal, \\
\hphantom{.}\hspace{34mm} Power-Law, and Kappa Distribution Functions'' \vspace{2mm} \\
\textbf{UIC College of Medicine Summer Science Forum}, \textit{Rockford, IL} \hfill August 2012\\
\textit{Poster presentation}, ``Synergistic Effects of c-Met and BRAF Inhibitors in \\
\hphantom{.}\hspace{34mm} Overcoming Tyrosine Kinase Inhibitor Resistance in \\
\hphantom{.}\hspace{34mm} Malignant Melanoma''

%\clearpage

%================ Teaching ===================%
\vspace{2mm}
\section{\mysidestyle Teaching Experience}
\textbf{TA, Princeton\hc{} \textit{Physics 104, General Physics II}} \hfill Spring 2021\vspace{2mm}\\
\textbf{TA, Princeton\hc{} \textit{Physics 103, General Physics I}} \hfill Fall 2020\vspace{2mm}\\
\textbf{TA, Princeton\hc{} \textit{Physics 115, Physics for Future Leaders}} \hfill Fall 2019\vspace{2mm}\\
\textbf{TA, Princeton\hc{} \textit{Physics 102, Introductory Physics II}} \hfill Spring 2019\vspace{2mm}\\
\textbf{TA, Princeton\hc{} \textit{Physics 103, General Physics I}} \hfill Fall 2018\\

%============== Outreach =====================%
\vspace{2mm}
\section{\mysidestyle Leadership \\ \& Service}
\textbf{Zoom a Princeton Physicist} \hfill 2022--2023\\
\textit{Spoke to high school physics classes about careers in research.} \vspace{2mm} \\
\textbf{Princeton Graduate Student Buddy Program} \hfill 2022--2023\\
\textit{Mentored incoming Princeton graduate students.} \vspace{2mm} \\
\textbf{Physics Unlimited Premier Competition} \hfill 2022\\
\textit{Volunteered to help with a high school physics competition.} \vspace{2mm} \\
\textbf{Princeton Physics Ambassadors} \hfill 2021--2023\\
\textit{Designed and staffed a series of webinars about graduate school, aimed \\
at students from communities historically underrepresented in physics.} \vspace{2mm} \\
\clearpage
\textbf{Princeton Society of Physics Students Mentorship Program} \hfill 2018--2023\\
\textit{Mentored physics majors as they started coursework and the search for \\
research opportunities.}\vspace{2mm} \\
\textbf{ReMatch Peer Mentor} \hfill 2018--2019\\
\textit{Mentored freshmen and sophomores as they started their first research \\
experiences in science.} \vspace{2mm} \\
\textbf{Cosmology for Kids} \hfill 2018\\
\textit{Presented and explained cosmology-themed physics demonstrations to \\
children of all ages and their parents.} \vspace{2mm} \\
\textbf{YMCA of Trenton STEM Camp} \hfill 2018\\
\textit{Designed a curriculum and presented a series of activities aimed to \\
make science accessible and interesting for children aged 5--13, mainly \\
from communities underrepresented in STEM.} \vspace{2mm} \\
\textbf{UIUC Physics Peer Mentor} \hfill 2016\\
\textit{Mentored incoming physics majors during their first semesters of college.} \vspace{2mm} \\

%============== Refereeing ===================%
\section{\mysidestyle Referee}
\textbf{The Astrophysical Journal} \hfill 2023--Present

\end{resume}   
\end{document}